FATE summary results

### 2019-10-09 paper draft.Rmd
Trying to extract HMM results

@@

>>>>

# run each trend sequentially through the regimes
# code to identify (1) number of changes and (2)
# where those change points occur.
set.seed(99)
f1 = find_regimes(y = y[1,], sds = sd_y[1,], max_regimes = 5)

@@

```{r}
# try to extract annual P of each state!
    # gamma_tk <- rstan::extract(f1$best_model, pars = "gamma_tk")[[1]]
    # mu_k <- rstan::extract(f1$best_model, pars = "mu_k")[[1]]
    # l <- apply(gamma_tk, 2:3, quantile, probs = probs[[1]])
    # u <- apply(gamma_tk, 2:3, quantile, probs = probs[[2]])
    # med <- apply(gamma_tk, 2:3, quantile, probs = 0.5)
